### 2021-12-12 thesis/tex/conclusion.tex
updated, and added worse s24 fig

\chapter{Conclusion}\label{ch:conc}
TBD
% TODO Conclusion:
% We produced the conclusion plots, and ic is insensitive to any impact if th34.
% NSI: which detector is more sensitive? Add paragraph on what parameters that PINGU can measure (in future tense). Write what constrain which parameters?
% Include effect on system uncertainty on PINGU. Compare with other measurements. Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
% Reference papers on PINGU, NSI. And NSI from Llong baseline experiments. Include reference to DUNE from ESS paper with S+T+M.

>>>>

\chapter{Conclusion}\label{ch:conc}
We were able to simulate the IceCube experiment with 86 strings, with our $3+0$ hypothesis shown against the IceCube Monte Carlo in Fig~\ref{fig:IC_MC_norm}. 
We normalized against the Monte Carlo, and produced the exclusion contour between the sterile neutrino parameters $\dm[41]$ and $\theta_[24]$ in Fig~\ref{fig:error_tuning}.
We found that the data is consistent with the $3+0$ hypothesis, with deviations up to 6\% at $\SI{10}{\TeV}$.
We also investigated the case when $\theta_{24} = \theta{34}$, and which produced an identical exclusion contour as in the case with $\theta_{34}=0$. This 
observation makes us conclude that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to observe 
an impact of $\theta_{34}$.

% TODO Conclusion:
% We produced the conclusion plots, and ic is insensitive to any impact if th34.
% NSI: which detector is more sensitive? Add paragraph on what parameters that PINGU can measure (in future tense). Write what constrain which parameters?
% Include effect on system uncertainty on PINGU. Compare with other measurements. Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
% Reference papers on PINGU, NSI. And NSI from Llong baseline experiments. Include reference to DUNE from ESS paper with S+T+M.

### 2021-12-12 thesis/tex/nsiResults.tex
updated, and added worse s24 fig

Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
% TODO: Write a few lines about the plots 5.4 and 5.5
\begin{figure}
   \begin{center}
      \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon. $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero.Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
   \end{center}
\end{figure}

%TODO: PINGU values are the same. Fill in empty values
{\renewcommand{\arraystretch}{1.0}
 \begin{table}
   \begin{center}
      \begin{tabular}{lcc}
         \hline
         Parameter & Best 90\% CL & Best $3\sigma$\\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017]  \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
         $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] \\
         $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] \\
         $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore} \\
         $\emt$ &  [-0.029, 0.007] &          [0.026] \\
         \hline
         \vspace{2em}
      \end{tabular}
      \begin{tabular}{lcc}
         \hline
         Parameter & Baseline 90\% CL & Baseline $3\sigma$ \\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.009, 0.01] &  [-0.015, 0.018]  \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &    [-0.046, 0.054] &         [-0.065]  \\
         $\emt$ &     [-0.009, 0.01] &  [-0.015, 0.018]  \\
         $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16]    \\
         $\eet$ &    [-0.10, 0.11] &  [-0.19, 0.18]  \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore}\\
         $\emt$ &   [-0.029, 0.007] &          [0.026] \\
         \hline
         \vspace{2em}
      \end{tabular}
      \begin{tabular}{lcc}
         \hline
         Parameter & Worst 90\% CL & Worst $3\sigma$\\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &   [-0.01, 0.011] &   [-0.017, 0.02] \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &    [-0.049, 0.057] &          [-0.07] \\
         $\emt$ &     [-0.01, 0.011] &   [-0.017, 0.02] \\
         $\eem$ &   [-0.14, 0.11] &   [-0.23, 0.18] \\
         $\eet$ &   [-0.13, 0.13] &  [-0.23, 0.12] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore}\\
         $\emt$ &   [-0.029, 0.007] &          [0.026] \\
         \hline
      \end{tabular}
      \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. $\dm[31]$ and $\theta_{23}$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero. Best, baseline, and worst refer to 
      the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
   \end{center}
\end{table}

\begin{table}
   \centering
   \begin{tabular}{lcc}
      \hline
      Parameter & Best 90\% CL & Best $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &  [-0.054, 0.067] &               [] \\
      $\emt$ &  [-0.029, 0.007] &          [0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] \\
      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] \\
      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013]  \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Baseline 90\% CL & Baseline $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &   [-0.054, 0.067] &               []\\
      $\emt$  &  [-0.029, 0.007] &          [0.026]  \\
      $\eem$ &    [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &    [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
      $\emt$ &    [-0.01, 0.006] &  [-0.016, 0.014] \\
      $\eem$ &    [-0.071, 0.086] &  [-0.149, 0.141]  \\
      $\eet$ &   [-0.061, 0.103] &  [-0.131, 0.155] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.01, 0.006] &  [-0.016, 0.014] \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &    [-0.054, 0.067] &               [] \\
      $\emt$ &    [-0.029, 0.007] &          [0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &     [-0.039, 0.05] &          [-0.06] \\
      $\emt$ &  [-0.011, 0.007] &  [-0.017, 0.015] \\
      $\eem$ &   [-0.082, 0.097] &  [-0.17, 0.16] \\
      $\eet$ &   [-0.067, 0.11] &  [-0.15, 0.17] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.011, 0.007] &  [-0.017, 0.015] \\
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. $\dm[31]$ and $\theta[23]$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
   Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

%TODO: compare results, fix tables

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm[31]$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
\newpage

 \begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.47\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.51\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
    \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years.}
\end{figure}
%TODO 5.6 is small, fix labels
There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI. For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the interaction Lagrangian respects lepton number conservation. 
The PMNS matrix, on the other hand, has off-diagonal elements because the kinetic Lagrangian breaks this symmetry. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
but this is not feasible. Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$. We let $\ett=0$ because we saw that it did not influence the other parameters. 
We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}. We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical. 
Hence, we can see that no relationship exists between them. With $\eet - \eem$, however, the contours are assuming a different shape. The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.
Thus, we can draw the conclusion that, given $\ett = 0$, PINGU might expect to observe that $\eem$ and $\emt$ are anti-correlated while we expect no significant correlation
to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$.

\begin{figure}
   \includegraphics[scale=0.5]{figures/PINGU_2D_all_f0.pdf}
   \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out. The values of the standard oscillation parameters 
   are taken from NuFit~\cite{nufit}.}\label{fig:PINGU_2D}
\end{figure}

>>>>

Comparing the PINGU and the DeepCore results in Fig.~\ref{fig:3D_NO}, we note that the best-fit for each NSI parameter for the PINGU experiment is expected to be zero. This is because the `data' we generated during 
the PINGU simulations assume no NSI since they have yet to be observed in nature. This introduces a non-NSI bias in all joint analyses which include PINGU
since PINGU has stronger statistics than DeepCore and will thus pull the joint $\chi^2$ towards $\epsilon =0$.
% TODO: Write a few lines about the plots 5.4 and 5.5
\begin{figure}
   \begin{center}
      \includegraphics[scale = 0.7]{figures/joint_3D_NO.pdf}
      \caption{Confidence regions for PINGU and DeepCore scenarios listed in Table~\ref{table:syst_errors}, with their joint $\Delta \chi^2$ in maroon. $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
      parameters not shown in each panel are fixed to zero. 
      IceCube tracks only reveal $\emt$, and are displayed separately in Fig.~\ref{fig:IC_3D}. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:3D_NO}
   \end{center}
\end{figure} 
\begin{figure}
   \begin{center} 
      \includegraphics[width=0.8\textwidth]{figures/PID_3D_emt.pdf}
      \caption{IceCube $\emt$ $\Delta \chi^2$ regions for scenarios as defined in Table~\ref{table:syst_errors}.
    $\dm[31]$ and $\theta_{23}$ and have been marginalized out, and all other NSI 
    parameters other than $\emt$ are fixed to zero. Dotted lines are the 90\% and $3\sigma$ CL levels.}\label{fig:IC_3D}
   \end{center}
\end{figure}

%TODO: PINGU values are the same. Fill in empty values
{\renewcommand{\arraystretch}{1.0}
 \begin{table}
   \begin{center}
      \begin{tabular}{lcc}
         \hline
         Parameter & Best 90\% CL & Best $3\sigma$\\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.0080, 0.0090] &  [-0.014, 0.017]  \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] \\
         $\emt$ &  [-0.0080, 0.0090] &  [-0.014, 0.017] \\
         $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] \\
         $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore} \\
         $\emt$ &  [-0.029, 0.0070] &  [-0.041, 0.026] \\
         \hline
         \vspace{2em}
      \end{tabular}
      \begin{tabular}{lcc}
         \hline
         Parameter & Baseline 90\% CL & Baseline $3\sigma$ \\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &  [-0.0090, 0.010] &  [-0.015, 0.018]  \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &    [-0.046, 0.054] &  [-0.065, 0.073]  \\
         $\emt$ &     [-0.0090, 0.010] &  [-0.015, 0.018]  \\
         $\eem$ &  [-0.11, 0.094] &  [-0.20, 0.16]    \\
         $\eet$ &    [-0.10, 0.11] &  [-0.19, 0.18]  \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore}\\
         $\emt$ &   [-0.029, 0.0070] & [-0.041, 0.026] \\
         \hline
         \vspace{2em}
      \end{tabular}
      \begin{tabular}{lcc}
         \hline
         Parameter & Worst 90\% CL & Worst $3\sigma$\\
         \hline & \multicolumn{2}{c}{IceCube}  \\
         $\emt$ &   [-0.010, 0.011] &   [-0.017, 0.020] \\\\
         & \multicolumn{2}{c}{DeepCore}\\ [0.3em]
         $\ett$ &    [-0.049, 0.057] &  [-0.070, 0.078] \\
         $\emt$ &     [-0.010, 0.011] &   [-0.017, 0.020] \\
         $\eem$ &   [-0.14, 0.11] &   [-0.23, 0.18] \\
         $\eet$ &   [-0.13, 0.13] &  [-0.23, 0.12] \\\\
         &\multicolumn{2}{c}{IceCube + DeepCore}\\
         $\emt$ &   [-0.029, 0.007] & [-0.041, 0.026] \\
         \hline
      \end{tabular}
      \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. $\dm[31]$ and $\theta_{23}$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero. Best, baseline, and worst refer to 
      the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
   \end{center}
\end{table}

\begin{table}
   \centering
   \begin{tabular}{lcc}
      \hline
      Parameter & Best 90\% CL & Best $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &  [-0.054, 0.067] & [-0.089, 0.10] \\
      $\emt$ &  [-0.029, 0.0070] & [-0.041, 0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] \\
      $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013] \\
      $\eem$ &   [-0.060, 0.077] &  [-0.13, 0.13] \\
      $\eet$ &  [-0.052, 0.095] &  [-0.11, 0.14] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &  [-0.0090, 0.0060] &  [-0.015, 0.013]  \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Baseline 90\% CL & Baseline $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &   [-0.054, 0.067] & [-0.089, 0.10]\\
      $\emt$  &  [-0.029, 0.0070] & [-0.041, 0.026] \\
      $\eem$ &    [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &    [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &    [-0.038, 0.048] &  [-0.058, 0.067] \\
      $\emt$ &    [-0.010, 0.0060] &  [-0.016, 0.014] \\
      $\eem$ &    [-0.071, 0.086] &  [-0.15, 0.14]  \\
      $\eet$ &   [-0.061, 0.10] &  [-0.13, 0.16] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.010, 0.006] &  [-0.016, 0.014] \\
      \hline
      %\vspace{0.5em}
   \end{tabular}
   \begin{tabular}{lcc}
      \hline 
      Parameter & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{2}{c}{PINGU} \\
      $\ett$ &    [-0.054, 0.067] & [-0.089, 0.10] \\
      $\emt$ &    [-0.029, 0.007] & [-0.041, 0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{2}{c}{DeepCore + PINGU} \\
      $\ett$ &     [-0.039, 0.050] & [-0.06, 0.07] \\
      $\emt$ &  [-0.011, 0.0070] &  [-0.017, 0.015] \\
      $\eem$ &   [-0.082, 0.097] &  [-0.17, 0.16] \\
      $\eet$ &   [-0.067, 0.11] &  [-0.15, 0.17] \\\\
      & \multicolumn{2}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &   [-0.011, 0.0070] &  [-0.017, 0.015] \\
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. $\dm[31]$ and $\theta[23]$ have been marginalized out, and all other NSI parameters other than the one shown for each row are set to zero.
   Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

%TODO: compare results

\begin{table}
   \begin{center}
   \begin{tabular}{lccc}
           \hline \hline & \multicolumn{3}{c} {\text {Best fit}} \\
           \cline { 2 - 4 } Parameter & $\dm[31]$ & $\theta_{23}$  & $\epsilon$  \\
           \hline \multicolumn{3}{c} {\hspace{2.5cm} DeepCore }  \\[0.1em]
           $\ett$ &  2.435 & 47.84 & 0.0125 \\
           $\emt$ &  2.435 & 43.97 & -0.005 \\
           $\eem$ &  2.435 & 43.97 & 0 \\
           $\eet$ &  2.435 & 43.97  & 0.05 \\\\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube } \\
           $\emt$ &  2.435 & 51.70 & 0 \\
           \multicolumn{3}{c} {\hspace{2.5cm} IceCube + DeepCore } \\
           $\emt$ &  2.517 & 43.97 & -0.01 \\
           \hline
           \hline
   \end{tabular}
   \end{center}
   \caption{Best fit points for $\dm[31]$ and $\theta_{23}$ are given in units of $\si{10^{-3}\eV\squared}$ and
   degrees, respectively.}\label{table:bestfit}
\end{table}
\newpage

 \begin{figure}[t]
   \begin{center}
      \begin{subfigure}{0.44\textwidth}
         \includegraphics[width=1\linewidth]{figures/PINGU_event_pulls.pdf}
         \caption{PINGU}\label{fig:PINGU_event_pulls}
      \end{subfigure}
      \begin{subfigure}{0.54\textwidth}
         \includegraphics[width=1\linewidth]{figures/DC_event_pulls.pdf}
         \caption{DeepCore}\label{fig:DC_event_pulls}
      \end{subfigure}
    \end{center}
   \caption{Expected pulls of the form $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ for PINGU and DeepCore after 3 years of data. 
   Each row has only one NSI non-zero parameter, with the first row having $\ett= -0.07$, second $\emt = -0.03$, third $\eem = -0.3$, and fourth $\eet = -0.3$.
   We clearly see the increased statistics of the PINGU detector, especially in cascade events. The low values of $\ett$ and $\emt$ produce a weak pull in DeepCore,
   while PINGU can be expected to observe multiple regions of strong pulls for $\emt$, $\eem$, and $\eet$.}\label{fig:event_pulls}
\end{figure}

We plot the event pull $(N_{NSI} - N_{SI})/\sqrt{N_{SI}}$ where $N_{(N)SI}$ are the numbers of expected events
assuming (non-)standard interactions in Fig.~\ref{fig:event_pulls}. This gives the normalized difference in the
number of expected events at the detector, and illustrates the expected sensitivity of DeepCore for the NSI parameters.

Now we will compare the probability plots with the final event counts in DeepCore. It is not enough to only study the effect at probability level, since that is in true quantities. 
Since the detector data comes in reconstructed quantities, it might be the case that a feature at probability level gets averaged out in the reconstruction, and not showing up at all in the data. 
In general, features showing at probability level are can be 
averaged out at reconstruction if they occur in the rapidly oscillating part of single-digit \si{\GeV} energies.

The top right panel shows a surplus of DeepCore track events at \SIrange{20}{30}{\GeV} for through-going neutrinos when we turn on $\ett$. This is what we expected from the bottom right panel in Fig.~\ref{fig:emt_ett_probs}, where we saw that we had an increase in $\anm$ survival probability at \SIrange{20}{40}{\GeV}.

The third right panel shows the expected event pull for $\eem$. Comparing with the probabilities in Fig.~\ref{fig:eem_eet_probs}, we see that the surplus of the $\anm$ survival in the \SIrange{20}{30}{\GeV} and the deficit above \SI{40}{\GeV} is intact, while the \SI{10}{\GeV} $\nm$ deficit is completely averaged out.

%TODO 5.6 is small, fix labels
There is no reason for us to assume that only one NSI parameter exists in Nature, unless we impose a symmetry on the gauge group which generates NSI. For example, the matter potential matrix in our Hamiltonian from Eq.~\eqref{eq:V_matrix} is diagonal since the 
interaction Lagrangian respects lepton flavor conservation. So ideally, we would simulate a grid where all NSI parameters are allowed to vary, 
but this is not feasible. Thus, we take we set $\ett = 0$ and let $\emt,\eem,\eet$ vary, along with $\dm[31]$ and $\theta_{23}$. We let $\ett=0$ because we saw that it did not influence the other parameters. 
We then marginalize out the standard oscillation parameters and one of the NSI parameters and plot the remaining two in Fig.~\ref{fig:PINGU_2D}. We see that the pairs $\eem - \emt$ and $\eet - \emt$ are symmetrical. 
Hence, we can see that no relationship exists between them. With $\eet - \eem$, however, the contours are assuming a different shape. The contour allows positive values of $\eet$ and $\eem$ to a greater degree than mixed or negative values.
Thus, we can draw the conclusion that, given $\ett = 0$, PINGU might expect to observe that $\eem$ and $\emt$ are anti-correlated while we expect no significant correlation
to be be seen between the pairs $\emt - \eem$, and $\emt - \eet$. This is consistent with our observation of the effect of these parameters on $\Pme$ in  Fig.~\ref{fig:eem_eet_prob}, from which we 
saw that $\eem$ and $\eet$ strongly affect $\Pme$ for single-digit \si{\GeV} energies.

\begin{figure}
   \includegraphics[scale=0.5]{figures/PINGU_2D_all_f0.pdf}
   \caption{Allowed regions for some of the NSI parameters after three years of PINGU data, assuming no uncorrelated systematic error. All plots are made with $\ett = 0$. The two
   standard oscillation parameters $\dm[31]$ and $\theta_{23}$ along with the one NSI parameter not shown have been marginalized out. We observe an anti-correlation between $\eem$ and $\eet$,
   consistent with our observation of the effect of these parameters on $\Pme$ in  Fig.~\ref{fig:eem_eet_prob}.
   The values of the standard oscillation parameters 
   are taken from NuFit~\cite{nufit}.}\label{fig:PINGU_2D}
\end{figure}
